\propertitle

### 2019-07-11 maxNt_v5.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-07-10T14:04:12+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal network\\ from subnetwork data%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

We therefore want to assess how well the maximum-entropy distributions of
\fig~\ref{fig:plots_6mom} answer our two questions above. We do this by
sampling from the probability density $\pf(\yF \| \yD \yI)$ through
Markov-chain Monte Carlo. The density is
\begin{equation}
  \label{eq:density_proportional}
  \pf(\yF \| \yD \yI) \propto
  \Nd(\ycm\yF \| \yc, \ycs)\;
  \Nd(\yd\yF \| 0, \yds)\;
  \exp[-\yL\;\ysh(\yF;\yR)]
\end{equation}

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-07-11T11:28:12+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal network\\ from subnetwork data%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

Let's therefore examine the full density $\pf(\yF \| \yD \yI)$ given by the
probability calculus. Its derivation is given in appendix***; here we
 discuss its mathematical features and examine the answers it
provides. Its expression,
\begin{equation}
  \label{eq:density_proportional}
  \pf(\yF \| \yD \yI) \propto \exp\biggl[
-  \frac{\abs{\ycm\yF - \yc}^{2}}{2\ycs^{2}}
-  \frac{\abs{\yd\yF}^{2}}{2\yds^{2}}
-\yL\;\ysh(\yF;\yR)\biggr],
\end{equation}
consists of three terms:

\textbullet\ The density $\exp[-\yL\;\ysh(\yF;\yR)]$ expresses our pre-data
uncertainty about the possible frequency distributions. Here
$\ysh(\yF;\yR)\defd \sum_{\yA}\yFF_{\yA}\ln(\yFF_{\yA}/\yRR_{\yA})$ is the
relative entropy or discrimination information
\citep{kullback1987,jaynes1963,hobson1969,hobsonetal1973}, $\yR$ is a
reference distribution, and $\yL$ a positive parameter. This density
expresses a belief proportional to the number of ways in which the
frequency distribution $\yF$ can be realized if we assume that the
activities appear with frequencies $\yR$ in the long run, as can be seen
using Stirling's approximation. For $\yR$ we choose the uniform
distribution, but any biologically sensible distribution, such as one
decreasing exponentially with the activity, leads to the same final
results. The parameter $\yL$ roughly represents the number of data points
necessary to change our initial belief, and we set it equal to $50$. This
density is similar to an \enquote{entropic prior}
\citep{rodriguez1991,skilling1998,catichaetal2004,portamana2017}[see
esp.][\sect~3]{neumann2007}.

\textbullet\ The previous density is corrected by the normal density
$\exp\Bigl(-\frac{\abs{\yd\yF}^{2}}{2\yds^{2}}\Bigr)$, where the matrix
$\yd$ is the discrete equivalent of a fourth-order derivative
operator. %ref?
This density expresses our belief, hinging on biological arguments, that
the frequency distribution should be somewhat smooth, without huge
discontinuities between one activity level and the next. The fourth
derivative is chosen because it still allows for the presence of modulated
maxima and minima more than derivatives of lower order do. The standard
deviation $\yds$ is such that the smoothness of the maximum-entropy
distribution, taken as a touchstone, is within two standard deviations.

\textbullet\ The normal density
$\exp\Bigl(-\frac{\abs{\ycm\yF - \yc}^{2}}{2\ycs^{2}}\Bigr)$ is the
likelihood of the frequency $\yF$ in view of the data $\yc$. The matrix
$\ycm$

The two densities above together express our pre-data beliefs about the
possible frequency distributions.

$\Nd(\ycm\yF \| \yc, \ycs)$ ***
